---
title: "test for translation"
author: "wwqi4realGitHub"
date: "4/4/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```


# function module

*before you run test on the code below, make sure you have all the files in correct paths*

*if edit, make sure you update the changes to Daily Report.R*

```{r}
translate_country = function(ut_data) {
  
  # wwqi4realGitHub Apr 4
  # ut_data: untranslated data frame, which is used for plots/tables
  # for the table part, Hubei translation is now supported
  # csv file is modified to support different country names (mainly for table 1 input)
  
  # support data input of 
  # plot: 2,3 (tho ggplot doesnt support Chinses char well)
  # table: 1,2,3
  
  
  
  # read in the CN-EN data
  cn_name = read_csv("./translation/world_cn.csv")
  en_name = read_csv("./translation/world_en.csv")
  
  # combine the two name dataframes
  # trans_name = cbind(cn_name, en_name)
  
  trans_name = full_join(cn_name, en_name, by = "id") %>% 
  janitor::clean_names() %>% 
  select(name_x, name_y) %>% 
  rename(Country_cn = name_x, 
         Country = name_y) %>% 
  unite("Country_bi", Country_cn:Country, sep = " ", remove = F)
  
  ut_data = ut_data %>% 
    mutate(Country = case_when(Country == "United Kingdom"~ "UK", 
                             TRUE ~ as.character(Country)))
  
  t_data = left_join(ut_data, trans_name, by = "Country") %>% 
    # in this step coercing warning will show up but dont worry
    mutate(Country =  as.factor(as.character(Country)), 
           Country_cn = as.factor(as.character(Country_cn)), 
           Country_bi = as.factor(as.character(Country_bi)))
  
  print("[Just if] Ignore the [coercing] warning, already taken care of")
  return(t_data)
}

translate_state = function(ut_data) {
  
  # wwqi4realGitHub Apr 5
  # ut_data: untranslated data frame, which is used for plots/tables
  
  # support data input of 
  # plot: 
  # table: 4,5,7
  
  state_cn = read_csv("./translation/state_translate.txt") %>% 
    rename(state = State_Full) %>% 
    janitor::clean_names()
  
  t_data = left_join(ut_data, state_cn, by = "state") %>% 
    select(state_cn, state, everything()) %>% 
    unite("state_bi", state_cn, state_abb, sep = " ", remove = F)
  
  return(t_data)
  
}

translate_country_colname = function(ut_data, x) {
  
  # wwqi4realGutHub
  # translate column names in table 1, 2, 3
  # x = number of the table
  
  if (x == 1) {
    
    t_data = ut_data %>% 
      select(Country_bi, Confirmed_Cases, Population, Crude_Incidence_Rate) %>% 
      rename("国家" = Country_bi, 
             "累计确诊病例" = Confirmed_Cases, 
             "国家/省份人口" = Population, 
             "粗发病率" = Crude_Incidence_Rate)
    
    return(t_data)
    
  } else if (x == 2) {
    t_data = ut_data %>% 
      select(Country_bi, Confirmed) %>% 
      rename("国家" = Country_bi, 
             "当日新增病例" = Confirmed)
    
    return(t_data)
  } else if (x == 3) {
    
    t_data = ut_data %>% 
      select(Country_bi, Deaths, Deaths_incremental, Fatality_rate) %>% 
      rename("国家" = Country_bi, 
             "累计死亡病例" = Deaths, 
             "较昨日" = Deaths_incremental, 
             "病死率" = Fatality_rate)
    
    return(t_data)
  } else {
    warning("x can only be 1, 2, 3; column name is NOT translated")
    return(ut_data)
  }
}

translate_state_colname = function(ut_data, x) {
  
  # wwqi4realGutHub
  # translate column names in table 4, 5, 6
  # x = number of the table
  
  if (x == 4) {
    
    t_data = ut_data %>% 
      select(state_bi, Confirmed, crude_incidence_rate, positive_rate, totalTestResults, totalTestResultsIncrease, pct_test) %>% 
      rename("州名" = state_bi, 
             "累计确诊" = Confirmed, 
             "粗发病率" = crude_incidence_rate, 
             "阳性率%" = positive_rate, 
             "累计检测" = totalTestResults, 
             "较昨日" = totalTestResultsIncrease, 
             "检测率" = pct_test)
    
    return(t_data)
    
  } else if (x == 5) {
    t_data = ut_data %>% 
      select(state_bi, Confirmed_Incremental, Percentage)
      rename("州名" = state_bi, 
             "当日新增" = Confirmed_Incremental, 
             "全美比率" = Percentage)
    
    return(t_data)
  } else if (x == 6) {
    
    t_data = ut_data %>% 
      select(state_bi, Deaths, Fatality_rate)
      rename("州名" = state_bi, 
             "累计死亡人数" = Deaths, 
             "病死率" = Fatality_rate)
    
    return(t_data)
  } else {
    
    warning("x can only be 4, 5, 6; column name is NOT translated")
    return(ut_data)
  }
}

tidy_uk = function(country_order) {
  country_order[which(country_order == "United Kingdom")] = "UK"
  
  return(country_order)
}
```

```{r no longer in use}
# not longer in use
# table 6 is deleted

# translate_table6 = function(ut_data) {
#   
#   # wwqi4realGitHub Apr 5
#   # ut_data: untranslated data frame, which is used for plots/tables
#   
#   # support data input of 
#   # plot: 
#   # table: 6
#   
#   state_cn = read_csv("./translation/state_translate.txt") %>% 
#     janitor::clean_names() %>% 
#     rename(state = state_abb)
#   
#   t_data = left_join(ut_data, state_cn, by = "state") %>% 
#   select(state_cn, state, everything()) %>% 
#   unite("state_bi", state_cn, state, sep = " ", remove = F)
#   
# }
```

# test module

### global countries and regions

the data below is from Daily Report.R 

To test, pls first run the R script to make sure the data is in Environment
```{r}
# change United Kingdom to UK
country_order[which(country_order == "United Kingdom")] = "UK"
```

```{r}
# Apr 4: pass for plot 2 and 3 data
pt2 = data_to_plot_confirmed %>% translate_country()

pt3 = data_to_plot_confirmed_increment %>% translate_country()
```

note0404: that table 1 use region as the 'country' name; considering use a different function
update0405: change the name in table 1 code, ignore note0403

```{r}
# 0404: pass for table 1
# 0405: no NA now, all check
  # tidy the form to template
# 0415: pass for UK abbreviation
tt1 = crude_incidence_rate_top %>% 
  translate_country() %>% 
  translate_country_colname(1)

ttt1 = crude_incidence_rate %>% 
  mutate(Country = case_when(Country == "United Kingdom"~ "UK", 
                             TRUE ~ as.character(Country)))
```

```{r}
# 0405 pass for table 2
  # tidy the form to template
# 0415: pass for UK abbreviation
tt2 = data_global_latest_confirmed_top %>% 
  rename("Country" = "Country/Region") %>% 
  translate_country() %>% 
  translate_country_colname(2)
```

```{r}
# 0405 pass for table 3
# 0415: pass for UK abbreviation
tt3 = data_global_latest_death_top %>% 
  rename("Country" = "Country/Region") %>% 
  translate_country() %>% 
  translate_country_colname(3)
```

### US states 

```{r}
# 0405 pass for table 4
tt4 = data_us_latest_confirm %>% 
  translate_state() %>% 
  translate_state_colname(4)
```

```{r}
# 0405 pass for table 5
tt5 = data_us_latest_incremental %>% 
  translate_state() %>% 
  translate_state_colname(5)
```

```{r}
# 0405 pass for table 7
# tt7 = data_us_latest_fatality %>% translate_state()
# 0405 update: removed table 6, now table 7 is called table 6 
tt6 = data_us_latest_fatality %>% 
  translate_state() %>% 
  translate_state_colname(6)
```

```{r}
# table 6 use different input, therefore use a separate function
# 0405 pass for table 6
# 0405 update table 6 is removed
# tt6 = data_us_positive_rate_avg %>% translate_table6()
```


---

