---
title: "For Chinese-Eng translation"
author: "wwqi4realGitHub"
date: "4/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

first read the csv files that needs to be updated with Chinese translation
```{r}
# input_country_population.csv
input_ctry_pop = read_csv("input_country_population.csv", locale = locale(encoding = "UTF-8"))
```


# wrangling country name data

import new data of corresponding Chinese name
data are downloaded from http://stefangabos.github.io/world_countries/
```{r}
cn_name = read_csv("./translation/world_cn.csv")
en_name = read_csv("./translation/world_en.csv")

# combine the two name dataframes
# trans_name = cbind(cn_name, en_name)
trans_name = full_join(cn_name, en_name, by = "id") %>% 
  janitor::clean_names() %>% 
  select(id, name_y, name_x) %>% 
  rename(Country_cn = name_x, 
         Country = name_y) %>% 
  select(id, Country_cn, Country) %>% 
  unite("Country_bi", Country_cn:Country, sep = " ", remove = F) %>% 
  mutate(Country = as.factor(Country), 
         Country_cn = as.factor(Country_cn), 
         Country_bi = as.factor(Country_bi))
```

combine the trans_name with the original data

note that I save the country id in the dataframe in case we need it in the future
but feel free to remove it
```{r}
input_ctry_pop_trans = left_join(input_ctry_pop, trans_name, by = "Country")
```

write the dataframe into csv file
```{r}
write_csv(new_ctry_pop, path = "input_country_population_translated.csv")
```



# wrangling state dataframe

modified from https://blogs.transparent.com/chinese/us-states-in-chinese/
```{r}
state_cn = read_csv("./translation/state_translate.txt")
input_state_pop = read_csv("input_state_population.csv", locale = locale(encoding = "UTF-8"))

```

join state_cn with input_state_population dataframe
```{r}
input_state_pop_translated = left_join(input_state_pop, state_cn, 
                                       by = "State_Full") %>% 
  select(State_Full, State_cn, State, Population) %>% 
  unite("State_bi", State_cn:State, sep = " ", remove = F)
```

wirte the translated state population dataframe into csv file

```{r}
write_csv(input_state_pop_translated, 
          path = "input_state_population_translated.csv")
```

* note: it seems that R tidyverse package has default encoding = "UTF-8"


